### 2024-10-26 slides/sections/locationeffects.Rmd
After review update

@@

```{r loceffectconbf, results='asis'}

ps_loc_diffs <- purrr::map_dfr(files, ~read_csv(.x) %>% 
                                 mutate(data = .x)) %>% 
  mutate(across(data, ~sub(".*/([^/]+)/[^/]+\\..*", "\\1", .)),
         across(data, ~recode(., 
                              "cato" = "CATO",
                              "spl2" = "SPL2", 
                              "gunnexp2" = "GE2",
                              #                "spl2_shift" = "*SPL2* (L1; shift + C)", 
                              "plantra" = "PLanTra",
                              "lift" = "LIFT",
                              "c2l1" = "C2L1"))) %>% 
  filter(!(str_detect(data, "SPL2") & lang == "ES"),
         !(str_detect(data, "CATO") & group == "dyslexic"),
         !(str_detect(data, "CATO") & task == "masked"),
         !(str_detect(data, "GE2") & xn == "masked"),
         param %in% c("delta", "theta")) %>%
  select(param, location, data, value) %>% 
  mutate(across(value, ~ifelse(param == "theta", .*-1, .))) %>% 
  pivot_wider(names_from = location, values_from = value) %>%
  unnest(-c(data, param)) %>% 
  mutate(diff.1 = `before sentence` - `before word`,
         diff.2 = `before word` - `within word`) %>% 
  summarise(across(starts_with("diff"), 
                   list(mean = mean, 
                        lower = lower, 
                        upper = upper, 
                        BF = BF)),
            .by = c(data, param))

tmp <- ps_loc_diffs %>% 
  pivot_longer(starts_with("diff"), names_to = c("diffid", ".value"), names_sep = "_") %>% 
  mutate(across(BF, ~ifelse(.>100, "> 100", as.character(round(.,2))))) %>% 
  select(-mean, -lower, -upper) %>% 
  pivot_wider(names_from = c(diffid, param), values_from = BF) %>% 
  select(data, contains("delta"), contains("theta")) %>% 
  arrange(data)

tmp %>% 
  kable(col.names = c("Dataset", rep(c("before sentence vs word", "before vs within word"), 2)),
        caption = "Values indicate BFs in support of the alternative hypothesis over the null hypothesis.", align = c("l", rep("r", 4))) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  add_header_above(c(" " = 1,
                     "Hesitation slowdown" = 2,
                     "Hesitation probability" = 2))

>>>>

```{r loceffectconbf}

ps_loc_diffs <- purrr::map_dfr(files, ~read_csv(.x) %>% 
                                 mutate(data = .x)) %>% 
  mutate(across(data, ~sub(".*/([^/]+)/[^/]+\\..*", "\\1", .)),
         across(data, ~recode(., 
                              "cato" = "CATO",
                              "spl2" = "SPL2", 
                              "gunnexp2" = "GE2",
                              #                "spl2_shift" = "*SPL2* (L1; shift + C)", 
                              "plantra" = "PLanTra",
                              "lift" = "LIFT",
                              "c2l1" = "C2L1"))) %>% 
  filter(!(str_detect(data, "SPL2") & lang == "ES"),
         !(str_detect(data, "CATO") & group == "dyslexic"),
         !(str_detect(data, "CATO") & task == "masked"),
         !(str_detect(data, "GE2") & xn == "masked"),
         param %in% c("delta", "theta")) %>%
  select(param, location, data, value) %>% 
  mutate(across(value, ~ifelse(param == "theta", .*-1, .))) %>% 
  pivot_wider(names_from = location, values_from = value) %>%
  unnest(-c(data, param)) %>% 
  mutate(diff.1 = `before sentence` - `before word`,
         diff.2 = `before word` - `within word`) %>% 
  summarise(across(starts_with("diff"), 
                   list(mean = mean, 
                        lower = lower, 
                        upper = upper, 
                        BF = ~log(BF(.)))),
            .by = c(data, param))

tmp <- ps_loc_diffs %>% 
  pivot_longer(starts_with("diff"), names_to = c("diffid", ".value"), names_sep = "_") %>% 
  #mutate(across(BF, ~ifelse(.>100, "> 100", as.character(round(.,2))))) %>% 
  mutate(across(BF, ~round(.,2))) %>% 
  select(-mean, -lower, -upper) %>% 
  pivot_wider(names_from = c(diffid, param), values_from = BF) %>% 
  select(data, contains("delta"), contains("theta")) %>% 
  arrange(data)

tmp %>% 
  mutate(across(-data, ~cell_spec(., color = ifelse(. > 1 | . < 0, "white", "black"), 
                                  background = ifelse(. > 1, "blue",
                                                  ifelse(. < 0, "red", "white"))))) %>% 
  kable(col.names = c("Dataset", rep(c("before sentence vs word", "before vs within word"), 2)),
        caption = "Values indicate log BFs in support of the alternative hypothesis over the null hypothesis.", 
        align = c("l", rep("r", 4)),
        escape = F,
        format = "html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  add_header_above(c(" " = 1,
                     "Hesitation slowdown" = 2,
                     "Hesitation probability" = 2)) %>% 
  row_spec(0:6, extra_css = "line-height: 2.25;")  
```

@@

### 2024-10-26 slides/sections/modelcomparisons.Rmd
After review update

```{r loos, results='asis'}
mc %>% 
  select(dataset, Comparison = model, elpd_diff_ratio) %>%
  pivot_wider(names_from = Comparison, values_from = elpd_diff_ratio) %>%
  mutate(across(-dataset, ~" ")) %>% 
  rename(`Data set` = dataset) %>% 
  select(1, 4, 3, 2) %>% 
  kable(align = c("l", rep("r", 3)),
        caption = "Vales are the absolute ratio of the difference in predictive performance measured as $\\widehat{elpd}$ and its standard error $\\mid\\frac{\\Delta\\widehat{elpd}}{\\text{SE}}\\mid$ which corresponds to the $z$-score of the difference between models [@sivula2020uncertainty].") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  row_spec(0:6, extra_css = "line-height: 2.25;")  
```

@@

```{r loos2, results='asis'}
mc %>% 
  select(dataset, Comparison = model, elpd_diff_ratio) %>%
  pivot_wider(names_from = Comparison, values_from = elpd_diff_ratio) %>%
  rename(`Data set` = dataset) %>% 
  select(1, 4, 3, 2) %>% 
  kable(align = c("l", rep("r", 3)),
        caption = "Vales are the absolute ratio of the difference in predictive performance measured as $\\widehat{elpd}$ and its standard error $\\mid\\frac{\\Delta\\widehat{elpd}}{\\text{SE}}\\mid$ which corresponds to the $z$-score of the difference between models [@sivula2020uncertainty].") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  row_spec(0:6, extra_css = "line-height: 2.25;")  
```

>>>>

```{r loos, results='asis'}
mc %>% 
  select(dataset, Comparison = model, elpd_diff_ratio) %>%
  pivot_wider(names_from = Comparison, values_from = elpd_diff_ratio) %>%
  mutate(across(-dataset, ~" ")) %>% 
  rename(`Data set` = dataset) %>% 
  select(1, 4, 3, 2) %>% 
  kable(align = c("l", rep("r", 3)),
        caption = "Values are the absolute ratio of the difference in predictive performance measured as $\\widehat{elpd}$ [@vehtari2015pareto; @vehtari2017practical] and its standard error $\\mid\\frac{\\Delta\\widehat{elpd}}{\\text{SE}}\\mid$ which corresponds to the $z$-score of the change in predictive performance [@sivula2020uncertainty].") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  row_spec(0:6, extra_css = "line-height: 2.25;")  
```

@@

```{r loos2, results='asis'}
mc %>% 
  select(dataset, Comparison = model, elpd_diff_ratio) %>%
  pivot_wider(names_from = Comparison, values_from = elpd_diff_ratio) %>%
  rename(`Data set` = dataset) %>% 
  select(1, 4, 3, 2) %>% 
  kable(align = c("l", rep("r", 3)),
        caption = "Values are the absolute ratio of the difference in predictive performance measured as $\\widehat{elpd}$ [@vehtari2015pareto; @vehtari2017practical] and its standard error $\\mid\\frac{\\Delta\\widehat{elpd}}{\\text{SE}}\\mid$ which corresponds to the $z$-score of the change in predictive performance [@sivula2020uncertainty].") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 14) %>% 
  row_spec(0:6, extra_css = "line-height: 2.25;")  
```

### 2024-10-26 slides/sections/modeloverview.Rmd
After review update

```{r models, results = 'asis'}
tibble(Models = str_c("M",1:4),
       Type = c("LMM", "LMM", "LMM", "MoG"),
       Description = c("Single distribution Gaussian",
                       "Single distribution log-Gaussian",
                       "Single distribution log-Gaussian with different variance components per text location",
                       "Two-distributions mixture of log-Gaussians.")) %>% 
  select(Models, Description) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 18) %>% 
  group_rows("Serial", 1, 3) %>% 
  group_rows("Parallel", 4, 4) %>% 
  row_spec(0:4, extra_css = "line-height: 2.25;")  %>% 
  column_spec(1, width = "3cm")

>>>>

```{r models, results = 'asis'}
tibble(Models = str_c("M",1:4),
       Type = c("LMM", "LMM", "LMM", "MoG"),
       Description = c("Single distribution Gaussian",
                       "Single distribution log-Gaussian",
                       "Single distribution log-Gaussian with different variance components per text location",
                       "Two-distributions mixture of log-Gaussians")) %>% 
  select(Models, Description) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"),
                full_width = T, 
                position = "right",
                font_size = 18) %>% 
  group_rows("Serial", 1, 3) %>% 
  group_rows("Parallel", 4, 4) %>% 
  row_spec(0:4, extra_css = "line-height: 2.25;")  %>% 
  column_spec(1, width = "3cm")

### 2024-10-26 slides/sections/mog_app.Rmd
After review update

@@

::: {style="margin-top:-20px; width: 96%;"}
```{r contpred}
inputPanel(
  sliderInput("beta_0", "Fluent typing", min = 100, max = 500, value = 150, ticks = FALSE),
  sliderInput("delta", "Hesitation slowdown", min = 50, max = 300, value = 100, ticks = FALSE),
  sliderInput("theta", "Hesitation probability", min = .001, max = .999, value = .3, ticks = FALSE),  
  switchInput("params", 
              size = "mini", 
              label = "Show means",
              onLabel = "on", 
              offLabel = "off", 
              labelWidth = "50%",
              width = "50%")
)

@@

  beta_0 <- log(200)
  beta_0 <- log(input$beta_0)
  delta <- 100
  delta <- input$delta
  theta <- .01
  theta <- input$theta
  beta_1 <- log(exp(beta_0) + delta)
  sigma <- .3
  sigma_diff <- .01
  sigmae <- sigma
  sigmae_p <- sigma + sigma_diff
  data <- data.frame(x = c(0, 1500))

  # Formula shown in plot
  formula <- list(~'iki'[i]~"~"~theta~paste("\u00B7")~  "logN("*beta~+~delta*","~sigma[2]^2*")",
                  ~+~"(1" - theta*")"~paste("\u00B7")~"logN("*beta*","~sigma[1]^2*")")

  p2 <- ggplot() +
    annotate("text", 
             x = 1.5, 
             y = seq(1, .25, 
                     length = length(formula)),
             label = formula, 
             parse = TRUE, 
             size = 6) +
    geom_rect(aes(xmin = -Inf, 
                  xmax = Inf, 
                  ymin = -Inf, 
                  ymax = Inf), 
              fill = "blue", 
              alpha = 0.05, 
              color = "black") +
    theme_void() +
    coord_cartesian(xlim = c(0, 3), ylim = c(-2.25, 2.4))

  if(input$params){
    beta_value <- round(exp(beta_0),0)
    theta_value <- dezero(theta, 2)
    delta_value <- round(delta, 2)
    beta_label <- substitute(beta==beta0, list(
      beta0 = beta_value))
    theta_label <- substitute(theta==theta_value, list(
      theta_value = theta_value))
    delta_label <- substitute(delta==delta_value, list(
      delta_value = delta_value))

    p2 <- p2 + 
      annotate("text",
               x = 2.25,
               y = -1,
               label = deparse(beta_label), 
               parse = TRUE, 
               size = 6) +
      annotate("text",
               x = 2.25,
               y = -1.5,
               label = deparse(theta_label), 
               parse = TRUE, 
               size = 6) +
      annotate("text",
               x = 2.25,
               y = -2,
               label = deparse(delta_label), 
               parse = TRUE, 
               size = 6)

  }

  p1 <- ggplot(data, aes(x)) +
    stat_function(geom = "line", fun = plot_mix_comps,
                  size = size,
                  args = list(beta_0, sigmae, lam = 1 - theta)) +
    stat_function(geom = "line", fun = plot_mix_comps,
                  size = size,
                  args = list(beta_1, sigmae_p, lam = theta)) +
    geom_area(stat = "function", 
              fun = plot_mix_comps, 
              show.legend = T, 
              alpha = alpha, 
              size = size, 
              aes(fill = "Fluent typing"), 
              args = list(beta_0, sigmae, lam = 1 - theta)) +
    geom_area(stat = "function", 
              fun = plot_mix_comps, 
              show.legend = T, 
              alpha = alpha, 
              size = size,
              aes(fill = 'Hesitation ("Pause")'), 
              args = list(beta_1, sigmae_p, lam = theta)) +
    geom_segment(x = exp(beta_0), 
                 y = 0, 
                 xend = exp(beta_0), 
                 yend = Inf, 
                 colour = "darkred", 
                 size = 1,
                 alpha = alpha) +
    geom_segment(x = exp(beta_1), 
                 y = 0, 
                 xend = exp(beta_1), 
                 yend = Inf, 
                 colour = "darkred", 
                 size = 1,
                 alpha = alpha) +
    geom_segment(x = exp(beta_0),
                 y = 0.0065, 
                 xend = exp(beta_1), 
                 yend = 0.0065, 
                 colour = "blue", 
                 alpha = alpha,
                 size = 1,
                 arrow = arrow(length = unit(0.3, "cm"), 
                               ends = "both", 
                               type = "closed")) +
    scale_fill_manual(breaks = c("Fluent typing", 'Hesitation ("Pause")'),
                      values = c("#000000","#009E73")) +
    scale_x_continuous(labels = scales::comma, breaks = seq(0, 2500, 200)) +
    coord_cartesian(ylim = c(0, .007), 
                    xlim = c(0, 800)) +
    labs(title = "",
         fill = "Mixture components",
         x = "Inter-keystroke interval [in msecs]",
         y = "Density")

  p1 + p2 + 
    plot_layout(widths = c(3, 1.25)) + 
    plot_layout(guides = 'collect')

@@

>>>>

# Mixture model parameters

@@

::: {style="margin-top:-20px; width: 96%;"}
```{r contpred}
inputPanel(
  sliderInput("beta_0", "Fluent typing", min = 50, max = 500, value = 300, step = 10, ticks = FALSE),
  sliderInput("delta", "Hesitation slowdown", min = 50, max = 1500, value = 100, step = 50, ticks = FALSE),
  sliderInput("theta", "Hesitation probability", min = .001, max = .999, value = .3, step = .05, ticks = FALSE)  
  # switchInput("params", 
  #             size = "mini", 
  #             label = "Show means",
  #             onLabel = "on", 
  #             offLabel = "off", 
  #             labelWidth = "50%",
  #             width = "50%", 
  #             value = FALSE)
)

@@

  beta_0 <- log(200)
  beta_0 <- log(input$beta_0)
  delta <- 100
  delta <- input$delta
  theta <- .01
  theta <- input$theta
  beta_1 <- log(exp(beta_0) + delta)
  sigma <- .3
  sigma_diff <- .01
  sigmae <- sigma
  sigmae_p <- sigma + sigma_diff
  data <- data.frame(x = c(0, 2500))

  # Formula shown in plot
  # formula <- list(~'iki'[i]~"~"~theta~paste("\u00B7")~  "logN("*beta~+~delta*","~sigma[2]^2*")",
  #                 ~+~"(1" - theta*")"~paste("\u00B7")~"logN("*beta*","~sigma[1]^2*")")
  # 
  # p2 <- ggplot() +
  #   # annotate("text", 
  #   #          x = 1.5, 
  #   #          y = seq(1, .25, 
  #   #                  length = length(formula)),
  #   #          label = formula, 
  #   #          parse = TRUE, 
  #   #          size = 7) +
  #   geom_rect(aes(xmin = -Inf, 
  #                 xmax = Inf, 
  #                 ymin = -Inf, 
  #                 ymax = Inf), 
  #             fill = "blue", 
  #             alpha = 0.05, 
  #             color = "black") +
  #   theme_void() +
  #   coord_cartesian(xlim = c(0, 3), ylim = c(-2.25, 2.4))

  # if(input$params){
  #   beta_value <- round(exp(beta_0),0)
  #   theta_value <- dezero(theta, 2)
  #   delta_value <- round(delta, 2)
  #   beta_label <- substitute(beta==beta0, list(
  #     beta0 = beta_value))
  #   theta_label <- substitute(theta==theta_value, list(
  #     theta_value = theta_value))
  #   delta_label <- substitute(delta==delta_value, list(
  #     delta_value = delta_value))
  #   
  #   
  #   p2 <- p2 + 
  #     annotate("text",
  #              x = 2.25,
  #              y = -1,
  #              label = deparse(beta_label), 
  #              parse = TRUE, 
  #              size = 6) +
  #     annotate("text",
  #              x = 2.25,
  #              y = -1.5,
  #              label = deparse(theta_label), 
  #              parse = TRUE, 
  #              size = 6) +
  #     annotate("text",
  #              x = 2.25,
  #              y = -2,
  #              label = deparse(delta_label), 
  #              parse = TRUE, 
  #              size = 6)
  #   
  # }

  ggplot(data, aes(x)) +
    stat_function(geom = "line", fun = plot_mix_comps,
                  size = size,
                  args = list(beta_0, sigmae, lam = 1 - theta)) +
    stat_function(geom = "line", fun = plot_mix_comps,
                  size = size,
                  args = list(beta_1, sigmae_p, lam = theta)) +
    geom_area(stat = "function", 
              fun = plot_mix_comps, 
              show.legend = T, 
              alpha = alpha, 
              size = size, 
              aes(fill = "Fluent typing"), 
              args = list(beta_0, sigmae, lam = 1 - theta)) +
    geom_area(stat = "function", 
              fun = plot_mix_comps, 
              show.legend = T, 
              alpha = alpha, 
              size = size,
              aes(fill = 'Hesitation ("Pause")'), 
              args = list(beta_1, sigmae_p, lam = theta)) +
    geom_segment(x = exp(beta_0), 
                 y = 0, 
                 xend = exp(beta_0), 
                 yend = Inf, 
                 colour = "darkred", 
                 size = 1,
                 alpha = alpha) +
    geom_segment(x = exp(beta_1), 
                 y = 0, 
                 xend = exp(beta_1), 
                 yend = Inf, 
                 colour = "darkred", 
                 size = 1,
                 alpha = alpha) +
    geom_segment(x = exp(beta_0),
                 y = 0.0065, 
                 xend = exp(beta_1), 
                 yend = 0.0065, 
                 colour = "blue", 
                 alpha = alpha,
                 size = 1,
                 arrow = arrow(length = unit(0.3, "cm"), 
                               ends = "both", 
                               type = "closed")) +
    scale_fill_manual(breaks = c("Fluent typing", 'Hesitation ("Pause")'),
                      values = c("#000000","#009E73")) +
    scale_x_continuous(labels = scales::comma, breaks = seq(0, 2500, 200)) +
    coord_cartesian(ylim = c(0, .005), 
                    xlim = c(-10, 2100)) +
    labs(title = "",
         fill = "Mixture components",
         x = "Inter-keystroke interval [in msecs]",
         y = "Density")

#  p1 + p2 + 
#    plot_layout(widths = c(3, 1.25)) + 
#    plot_layout(guides = 'collect')

@@

## Parallel view: mixture of two processes {.smaller}

<div style="float: left; width: 40%;">

```{r fig.width=5}
# function for mixture models
plot_mix_comps <- function(x, mu, sigma, lam) lam * dnorm(x, mu, sigma)

# Parameters
data <- data.frame(x = c(50, 1500))
theta_conj <- .3
theta_simp <- .1
alpha <- 250
delta <- c(250, 500)
alpha2_w <- alpha + delta[1]
alpha2_s <- alpha + delta[2]
sigma <- 40
sigma_diff <- c(30, 60)
sigmae <- sigma
sigmae_p_w <- sigma + sigma_diff[1]
sigmae_p_s <- sigma + sigma_diff[2]

ggplot(data, aes(x)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = word_lbl),
                linewidth = linewidth,
                args = list(alpha, sigmae, lam = 1 - theta_simp)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = word_lbl),
                linewidth = linewidth,
                args = list(alpha2_w, sigmae_p_w, lam = theta_simp)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = word_lbl), alpha = .25, 
            args = list(alpha, sigmae, lam = 1 - theta_simp)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = word_lbl), alpha = .25, 
            args = list(alpha2_w, sigmae_p_w, lam = theta_simp)) +
  scale_color_manual(breaks = c(word_lbl, sent_lbl), values = ggthemes::colorblind_pal()(2)) +
  scale_fill_manual(breaks = c(word_lbl, sent_lbl), values = ggthemes::colorblind_pal()(2)) +
  scale_x_continuous(labels = scales::comma, 
                     limits = c(50, 1000), 
                     breaks = seq(0, 1500, 200)) +
  labs(x = "Interkey intervals [in ms]", 
       colour = "Text location",
       fill = "Text location") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

```
</div>

<div style="float: right; width: 50%;">
\
\
\
\

$$
\text{iki}_{i} \sim\text{ } \theta \times \text{log}\mathcal{N}(\beta + \delta, \sigma_{e'}^2) + \\
   (1 - \theta) \times \text{log}\mathcal{N}(\beta, \sigma_{e}^2)
$$

</div>

## Parallel view: mixture of two processes {.smaller}

<div style="float: left; width: 40%;">

```{r fig.width=5}
ggplot(data, aes(x)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = word_lbl),
                linewidth = linewidth,
                args = list(alpha, sigmae, lam = 1 - theta_simp)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = sent_lbl),
                linewidth = linewidth,
                args = list(alpha, sigmae, lam = 1 - theta_conj)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = word_lbl),
                linewidth = linewidth,
                args = list(alpha2_w, sigmae_p_w, lam = theta_simp)) +
  stat_function(geom = "line", fun = plot_mix_comps,
                aes(colour = sent_lbl),
                linewidth = linewidth,
                args = list(alpha2_s, sigmae_p_s, lam = theta_conj)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = word_lbl), alpha = .25, 
            args = list(alpha, sigmae, lam = 1 - theta_simp)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = sent_lbl), alpha = .15,
            args = list(alpha, sigmae, lam = 1 - theta_conj)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = word_lbl), alpha = .25, 
            args = list(alpha2_w, sigmae_p_w, lam = theta_simp)) +
  geom_area(stat = "function", fun = plot_mix_comps, aes(fill = sent_lbl), alpha = .15,
            args = list(alpha2_s, sigmae_p_s, lam = theta_conj)) +
  geom_curve(aes(x = alpha2_w, 
                 xend = alpha2_s, y = 0.0008, yend = 0.0015),
             curvature = -0.2, 
             size = .15,
             arrow = arrow(length = unit(0.3, "cm"))) +
  annotate("text", 
           x = (alpha2_w + alpha2_s)/2,
           y=.0022, 
           label=paste0("theta[diff]", "~and~", "delta[diff]"), size = 4, parse=TRUE) +
  scale_color_manual(breaks = c(word_lbl, sent_lbl), values = ggthemes::colorblind_pal()(2)) +
  scale_fill_manual(breaks = c(word_lbl, sent_lbl), values = ggthemes::colorblind_pal()(2)) +
  scale_x_continuous(labels = scales::comma, 
                     limits = c(50, 1000), 
                     breaks = seq(0, 1500, 200)) +
  labs(x = "Interkey intervals [in ms]", 
       colour = "Text location",
       fill = "Text location") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

```
</div>

<div style="float: right; width: 50%;">
\
\
\
\

$$
\text{iki}_{i} \sim\text{ } \theta_\text{location[i]} \times \text{log}\mathcal{N}(\beta + \delta_\text{location[i]}, \sigma_{e'_\text{location[i]}}^2) + \\
   (1 - \theta_\text{location[i]}) \times \text{log}\mathcal{N}(\beta, \sigma_{e_\text{location[i]}}^2)
$$

### 2024-10-26 slides/sections/sampledata.Rmd
After review update

```{r eval = F}
read_csv('tutorial/data/process_data_by_event.csv') %>% 
  filter(location != "post-paragraph", 
         !is.na(location),
         next_event_type == "production",
         event_type == "production",
         event_duration > 50,
         event_duration < 30000,
         session_no == 1) %>%
  drop_na(text) %>%
  mutate(across(text, str_to_lower)) %>% 
  filter(text %in% letters) %>% 
  mutate(.by = c(token, location), 
         idx = sample(n())) %>% 
  filter(idx <= 50) %>% 
  select(participant, iki = event_duration, location, pretext, text) %>% 
  mutate(across(location, ~recode(., 
                                  "within-word" = "within word",
                                  "post-word" = "before word",
                                  "post-sentence" = "before sentence"))) %>% 
  filter(participant %in% sample(unique(participant), 10)) %>% 
  mutate(recent_text = substr(pretext, 
                              start = nchar(pretext) - 40,
                              stop = nchar(pretext))) %>% 
  select(-pretext) %>% 
  rename(new_letter = text) %>% 
  relocate(participant, location, recent_text, new_letter, iki) %>% 
  write_csv("slides/data/sampledata.csv")
```

```{r}
data <- read_csv("slides/data/sampledata.csv")
slice(data, sample(nrow(data), size = 10))
```

## How are these data distributed?

```{r fig.width=10, fig.height=6}
ggplot(data, aes(x = iki, colour = location, fill = location)) +
  geom_density(alpha = .25) +
  scale_colour_colorblind() +
  scale_fill_colorblind() +
  scale_x_log10() 
```

>>>>

```{r eval = F, message=F}
read_csv('../../tutorial/data/process_data_by_event.csv') %>% 
  filter(location != "post-paragraph", 
         !is.na(location),
         next_event_type == "production",
         event_type == "production",
         event_duration > 50,
         event_duration < 30000,
         session_no == 1) %>%
  drop_na(text) %>%
  mutate(across(text, str_to_lower)) %>% 
  filter(text %in% letters) %>% 
  mutate(.by = c(token, location), 
         idx = sample(n())) %>% 
  filter(idx <= 20) %>% 
  select(participant, iki = event_duration, location, pretext, text) %>% 
  mutate(across(location, ~recode(., 
                                  "within-word" = "within word",
                                  "post-word" = "before word",
                                  "post-sentence" = "before sentence"))) %>% 
  filter(participant %in% sample(unique(participant), 10)) %>% 
  mutate(recent_text = substr(pretext, 
                              start = nchar(pretext) - 15,
                              stop = nchar(pretext))) %>% 
  select(-pretext) %>% 
  rename(new_letter = text) %>% 
  relocate(participant, location, recent_text, new_letter, iki) %>% 
  write_csv("../data/sampledata.csv")
```

```{r}
data <- read_csv("../data/sampledata.csv")
slice(data, sample(nrow(data), size = 20)) %>% 
  kable() %>% 
  kable_styling(full_width = T, font_size = 16)
```

## How are interkey intervals distributed?

```{r fig.width=10, fig.height=4.5}
ggplot(data, aes(x = iki, colour = location, fill = location)) +
  geom_density(alpha = .25) +
  scale_colour_colorblind() +
  scale_fill_colorblind() +
  scale_x_log10() 
```

## Usual practice

```{r fig.width=10, fig.height=4.5}
ggplot(data, aes(x = iki, colour = location, fill = location)) +
  geom_density(alpha = .25) +
  scale_colour_colorblind() +
  scale_fill_colorblind() +
  scale_x_log10() +
  geom_vline(xintercept = c(500, 1000, 2000), colour = "red", linetype = "dashed") +
  annotate(geom = "text",
           x = c(500, 1000, 2000), 
           y = c(1.5, 1.25, 1),
           label = str_c(c(500, 1000, 2000), " msecs")) +
  labs(y = "density")
```

## Usual practice

```{r echo = T}
data_with_pause <- data %>% 
  mutate(is_pause.500 = iki > 500,
         is_pause.1k = iki > 1000,
         is_pause.2k = iki > 2000)
```

```{r echo = T}
data_with_pause %>% 
  summarise(across(starts_with("is_pause"), list(prop = mean)), .by = location) %>% 
  rename_with(.fn = ~str_remove(., "^.+\\.")) %>% 
  arrange(location)
```

## Usual practice

```{r echo = T}
data_with_pause %>% 
  pivot_longer(starts_with("is_pause"), names_to = c(".value", "threshold"), names_sep = "\\.") %>% 
  filter(is_pause) %>% 
  summarise(avg = mean(iki), sd = sd(iki), n = n(), .by = c(threshold, location)) %>% 
  arrange(threshold)
```

### 2024-10-26 slides/sections/simulation.Rmd
After review update

- Simulate data from a single log-normal distribution
- Simulate data from a mixture of to log-normal distribution
- Data simulated with mixture process: 
  - Advantage for mixture model over single process model: $\Delta\widehat{elpd} =$ `r mixturedata`
- Data simulated with single process: 
  - Negligible difference between models: $\Delta\widehat{elpd} =$ `r singledata`

>>>>

- Simulate data from (i) a single log-normal distribution and (ii) a mixture of two log-normal distributions.
- Analysed both in (i) a single process model and (ii) a mixture model.
- Data simulated with mixture process: 
  - Advantage for mixture model over single process model: $\Delta\widehat{elpd} =$ `r mixturedata`
- Data simulated with single process: 
  - Negligible difference between models: $\Delta\widehat{elpd} =$ `r singledata`
